Pre-process China related and country counts

### 2022-07-31 02_clean_and_merge/03_02_Pre-process China related and country counts.Rmd
Update and rename Pre-process China related and country counts.Rmd to 03_02_Pre-process China related and country counts.Rmd

```{r}
Xinhua_2000 <- subset(df2_subset_China, df2_subset_China$year==2000)
#head(Xinhua_2000)
library(tidyverse)
#https://hbctraining.github.io/Intro-to-R/lessons/08_intro_tidyverse.html
#Xinhua_2000 <- Xinhua_2000 %>% 
#  rownames_to_column() %>% 
#  as_tibble()
```

>>>>

```{r}
## need to manually update the years and files
Xinhua_2000 <- subset(df2_subset_China, df2_subset_China$year==2000)
#head(Xinhua_2000)
library(tidyverse)
#https://hbctraining.github.io/Intro-to-R/lessons/08_intro_tidyverse.html
#Xinhua_2000 <- Xinhua_2000 %>% 
#  rownames_to_column() %>% 
#  as_tibble()
```
